Abstraction-averse programming

### 2024-03-01 latex/ms.tex
update dependencies

\section{Abstraction-averse programming}
The phrase "Abstraction-averse" is in contrast to "Abstraction-free" where would need to program in machine language (0s and 1s) exactly as the CPU sees them.
However "Abstraction-averse" recognizes the practical aspect of abstraction but instructs that the introduction/creation of abstractions should be avoided as much as possible.

>>>>

\section{Abstraction-averse programming}
Abstraction-averse is in contrast to Abstraction-free where would need to program in machine language (0s and 1s) exactly as the CPU sees them.
However Abstraction-averse recognizes the practical aspect of abstraction but instructs that the introduction/creation of abstractions should be avoided as much as possible.
